---
date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: true 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results Using Envelopment Model

```{r load_package, echo = FALSE, message = FALSE}

library(readr)
library(dplyr)
library(stringr)
library(kableExtra)
library(TRA)

schooldata <- read_csv("D:/PSU/DEA/BSD DEA Project/ETM 506/MPI Project/Processed Data/MPI_BDS_data.csv", show_col_types=F)|>
  mutate(School = substr(School, 1, nchar(School)-4))

```



### Efficiency Result for Academic Year 2018-19 

```{r, echo=FALSE}

sdata1819 <- as.data.frame(schooldata[,c(1,3,4,5,8,9)]) 

data1819 <- sdata1819[1:34,]

ND <- nrow(data1819)

DMUNames <- sdata1819[1:34,1] #use this format for DMU Names

# Extract Input variable
xdata <- as.matrix(data1819 [,2])

# Extract Output variables 
ydata <- as.matrix(data1819 [,3:6])

# Extract number of Input, Output and DMUs 
ND <- nrow(xdata) # Number of DMUs
NX <- ncol(xdata) # Number of Inputs (1 in this case)
NY <- ncol(ydata) # Number of Outputs (4 in this case)

# Assign row names for Input
rownames(xdata) <- DMUNames

# Assign row names for Outputs
rownames(ydata) <- DMUNames
 
Xnames <- colnames(xdata)
Ynames <- colnames(ydata)
                             
# Assign names for DMUs
DMUnames <-list(DMUNames)
Lambdanames <- paste0("$\\lambda_{S", 1:ND, "}$")

```


```{r, echo=FALSE,message = FALSE}
library(dplyr, quietly = TRUE) # For data organizing
library(ROI, quietly = TRUE) # R Optimization Interface
library(ROI.plugin.glpk, quietly = TRUE) # Connection to glpk as solver
library(ompr, quietly = TRUE) # Optimization Modeling using R
library(ompr.roi, quietly = TRUE) # Connective tissue
```




```{r, echo=FALSE}

# Need to remember to restructure the results matrices.

res.efficiency <- matrix(rep(-1.0, ND), nrow = ND, ncol = 1)
res.lambda     <- matrix(rep(-1.0, ND^2), nrow = ND,ncol = ND)
res.vweight    <- matrix(rep(-1.0, ND*NX), nrow=ND,ncol=NX) 
res.uweight    <- matrix(rep(-1.0, ND*NY), nrow=ND,ncol=NY) 

dimnames(res.efficiency) <- c(DMUnames,"VRS-IO")
dimnames(res.lambda)     <- c(DMUnames,DMUnames)

RTS<-"VRS"
for (k in 1:ND) {
  
  school_VRS <- MIPModel() |>
    add_variable(vlambda[j], j = 1:ND, type = "continuous",
                 lb = 0) |>
    add_variable(vtheta, type = "continuous") |>
    set_objective(vtheta, "min") |>
    add_constraint(sum_expr(vlambda[j] * xdata[j,i], j = 1:ND)
                   <= vtheta * xdata[k,i], i = 1:NX,
                   .show_progress_bar=FALSE ) |>
    add_constraint(sum_expr(vlambda[j] * ydata[j,r], j = 1:ND)
                   >= ydata[k,r], r = 1:NY,
                   .show_progress_bar=FALSE )
  if (RTS=="VRS") {school_VRS <- add_constraint(school_VRS,
                  sum_expr(vlambda[j],j = 1:ND) == 1) }
  
  #Returns to Scale
res1 <- solve_model(school_VRS, with_ROI(solver = "glpk"))
  
res.efficiency[k] <- get_solution(res1, vtheta)
res.lambda[k,] <- t(as.matrix(as.numeric(get_solution(res1, vlambda[j])[,3] )))

rduals  <- as.matrix(get_row_duals(res1))
res.vweight[k,] <- -1*rduals[1:NX]
res.uweight[k,] <- rduals[(NX+1):(NX+NY)]
}

```


```{r, echo=FALSE}

result_1819 <- res.efficiency

colnames(result_1819) = c("$\\theta^{VRS}$")

kbl (result_1819, booktabs=T, escape=F, longtable=T, digits=3, align='lc',
     caption="School Efficiency for Academic Year 2018-19 Based on Envelopment Model (IO-VRS)")          |>
  kable_styling(latex_options=c("HOLD_position","striped","repeat_header"))

```


### Efficiency Result for Academic Year 2020-21 

```{r, echo=FALSE}

sdata2021 <- as.data.frame(schooldata[,c(1,3,4,5,8,9)]) 

data2021 <- sdata2021[35:68,]

ND <- nrow(data2021)

DMUNames <- sdata2021[35:68,1] #use this format for DMU Names

# Extract Input variable
xdata <- as.matrix(data2021 [,2])

# Extract Output variables 
ydata <- as.matrix(data2021 [,3:6])

# Extract number of Input, Output and DMUs 
ND <- nrow(xdata) # Number of DMUs
NX <- ncol(xdata) # Number of Inputs (1 in this case)
NY <- ncol(ydata) # Number of Outputs (4 in this case)

# Assign row names for Input
rownames(xdata) <- DMUNames

# Assign row names for Outputs
rownames(ydata) <- DMUNames
 
Xnames <- colnames(xdata)
Ynames <- colnames(ydata)
                             
# Assign names for DMUs
DMUnames <-list(DMUNames)
Lambdanames <- paste0("$\\lambda_{S", 1:ND, "}$")

```


```{r, echo=FALSE}

# Need to remember to restructure the results matrices.

res.efficiency <- matrix(rep(-1.0, ND), nrow = ND, ncol = 1)
res.lambda     <- matrix(rep(-1.0, ND^2), nrow = ND,ncol = ND)
res.vweight    <- matrix(rep(-1.0, ND*NX), nrow=ND,ncol=NX) 
res.uweight    <- matrix(rep(-1.0, ND*NY), nrow=ND,ncol=NY) 

dimnames(res.efficiency) <- c(DMUnames,"VRS-IO")
dimnames(res.lambda)     <- c(DMUnames,DMUnames)

RTS<-"VRS"
for (k in 1:ND) {
  
  school_VRS <- MIPModel() |>
    add_variable(vlambda[j], j = 1:ND, type = "continuous",
                 lb = 0) |>
    add_variable(vtheta, type = "continuous") |>
    set_objective(vtheta, "min") |>
    add_constraint(sum_expr(vlambda[j] * xdata[j,i], j = 1:ND)
                   <= vtheta * xdata[k,i], i = 1:NX,
                   .show_progress_bar=FALSE ) |>
    add_constraint(sum_expr(vlambda[j] * ydata[j,r], j = 1:ND)
                   >= ydata[k,r], r = 1:NY,
                   .show_progress_bar=FALSE )
  if (RTS=="VRS") {school_VRS <- add_constraint(school_VRS,
                  sum_expr(vlambda[j],j = 1:ND) == 1) }
  
  #Returns to Scale
res2 <- solve_model(school_VRS, with_ROI(solver = "glpk"))
  
res.efficiency[k] <- get_solution(res2, vtheta)
res.lambda[k,] <- t(as.matrix(as.numeric(get_solution(res2, vlambda[j])[,3] )))

rduals  <- as.matrix(get_row_duals(res2))
res.vweight[k,] <- -1*rduals[1:NX]
res.uweight[k,] <- rduals[(NX+1):(NX+NY)]
}

```


```{r, echo=FALSE}

result_2021 <- res.efficiency

colnames(result_2021) = c("$\\theta^{VRS}$")
#c("$\\theta^{VRS}$")

kbl (result_2021, booktabs=T, escape=F, longtable=T, digits=3, align='lc',
     caption="School Efficiency for Academic Year 2020-21 Based on Envelopment Model (IO-VRS)")          |>
  kable_styling(latex_options=c("HOLD_position","striped","repeat_header"))

```


### Efficiency Result for Academic Year 2021-22 

```{r, echo=FALSE}

sdata2122 <- as.data.frame(schooldata[,c(1,3,4,5,8,9)]) 

data2122 <- sdata2122[69:102,]

ND <- nrow(data2122)

DMUNames <- sdata2122[69:102,1] #use this format for DMU Names

# Extract Input variable
xdata <- as.matrix(data2122 [,2])

# Extract Output variables 
ydata <- as.matrix(data2122 [,3:6])

# Extract number of Input, Output and DMUs 
ND <- nrow(xdata) # Number of DMUs
NX <- ncol(xdata) # Number of Inputs (1 in this case)
NY <- ncol(ydata) # Number of Outputs (4 in this case)

# Assign row names for Input
rownames(xdata) <- DMUNames

# Assign row names for Outputs
rownames(ydata) <- DMUNames
 
Xnames <- colnames(xdata)
Ynames <- colnames(ydata)
                             
# Assign names for DMUs
DMUnames <-list(DMUNames)
Lambdanames <- paste0("$\\lambda_{S", 1:ND, "}$")

```


```{r, echo=FALSE}

# Need to remember to restructure the results matrices.

res.efficiency <- matrix(rep(-1.0, ND), nrow = ND, ncol = 1)
res.lambda     <- matrix(rep(-1.0, ND^2), nrow = ND,ncol = ND)
res.vweight    <- matrix(rep(-1.0, ND*NX), nrow=ND,ncol=NX) 
res.uweight    <- matrix(rep(-1.0, ND*NY), nrow=ND,ncol=NY) 

dimnames(res.efficiency) <- c(DMUnames,"VRS-IO")
dimnames(res.lambda)     <- c(DMUnames,DMUnames)

RTS<-"VRS"
for (k in 1:ND) {
  
  school_VRS <- MIPModel() |>
    add_variable(vlambda[j], j = 1:ND, type = "continuous",
                 lb = 0) |>
    add_variable(vtheta, type = "continuous") |>
    set_objective(vtheta, "min") |>
    add_constraint(sum_expr(vlambda[j] * xdata[j,i], j = 1:ND)
                   <= vtheta * xdata[k,i], i = 1:NX,
                   .show_progress_bar=FALSE ) |>
    add_constraint(sum_expr(vlambda[j] * ydata[j,r], j = 1:ND)
                   >= ydata[k,r], r = 1:NY,
                   .show_progress_bar=FALSE )
  if (RTS=="VRS") {school_VRS <- add_constraint(school_VRS,
                  sum_expr(vlambda[j],j = 1:ND) == 1) }
  
  #Returns to Scale
res3 <- solve_model(school_VRS, with_ROI(solver = "glpk"))
  
res.efficiency[k] <- get_solution(res3, vtheta)
res.lambda[k,] <- t(as.matrix(as.numeric(get_solution(res3, vlambda[j])[,3] )))

rduals  <- as.matrix(get_row_duals(res3))
res.vweight[k,] <- -1*rduals[1:NX]
res.uweight[k,] <- rduals[(NX+1):(NX+NY)]
}

```


```{r, echo=FALSE}

result_2122 <- res.efficiency

colnames(result_2122) = c("$\\theta^{VRS}$")

kbl (result_2122, booktabs=T, escape=F, longtable=T, digits=3, align='lc',
     caption="School Efficiency for Academic Year 2021-22 Based on Envelopment Model (IO-VRS)")          |>
  kable_styling(latex_options=c("HOLD_position","striped","repeat_header"))

```


## MPI Results using `Benchmarking` Package
### Academic Year 2018-19 and 2020-21

```{r bench_1821, echo = FALSE, message = FALSE}

library(Benchmarking)

DMUNames <- schooldata[1:34,1] 
mpi_data <- schooldata[,c(1,3,4,5,8,9)]

x0 <- as.matrix(mpi_data [1:34,2])
y0 <- as.matrix(mpi_data [1:34,(3:6)])

x1 <- as.matrix(mpi_data [35:68,2])
y1 <- as.matrix(mpi_data [35:68,(3:6)])

m1 <- malmq(x0,y0,,x1,y1,,RTS="vrs", ORIENTATION = "in")

result1821 <- cbind(DMUNames,m1$e00,m1$e10,m1$e11,m1$e01,m1$ec,m1$tc,m1$m)
#e00 = efficincies for period 0 with reference technology from period 0
#e10 = efficincies for period 1 with reference technology from period 0
#e11 = efficincies for period 1 with reference technology from period 1
#e01 = efficincies for period 0 with reference technology from period 1


colnames(result1821) <- c("School", "E1819-T1819", "E2021-T1819", 
                      "E2021-T2021", "E1819-T2021", "PTEC", "TC", "MPI")

kable(result1821, booktabs = T, align = "lccccccc", digits = 3, longtable=T,
               caption = "Benchamrking Pacakge Results (IO-VRS): Academic Year 2018-19 and 2020-21") |>
  kable_styling(latex_options = c("repeat_header","HOLD_position","striped")) |>
  footnote(general = c("1819 = Academic Year 2018-19 and 2021 = Academic Year 2020-21",
                       "E1819-T1819 = Efficiency for academic year 2018-19 with reference technology from academic year 2018-19",
                       "E2021-T1819 = Efficiency for academic year 2020-21 with reference technology from academic year 2018-19",
                       "E2021-T2021 = Efficiency for academic year 2020-21 with reference technology from academic year 2020-21",
                       "E1819-T2021 = Efficiency for academic year 2018-19 with reference technology from academic year 2020-21"))

```

### Academic Year 2020-21 and 2021-22

```{r bench_2022, echo = FALSE, message = FALSE}

DMUNames <- schooldata[1:34,1] 
mpi_data <- schooldata[,c(1,3,4,5,8,9)]

x1 <- as.matrix(mpi_data [35:68,2])
y1 <- as.matrix(mpi_data [35:68,(3:6)])

x2 <- as.matrix(mpi_data [69:102,2])
y2 <- as.matrix(mpi_data [69:102,(3:6)])

m2 <- malmq(x1,y1,,x2,y2,,RTS="vrs", ORIENTATION = "in")

result2022 <- cbind(DMUNames,m2$e00,m2$e10,m2$e11,m2$e01,m2$ec,m2$tc,m2$m)
#e00 = efficincies for period 0 with reference technology from period 0
#e10 = efficincies for period 1 with reference technology from period 0
#e11 = efficincies for period 1 with reference technology from period 1
#e01 = efficincies for period 0 with reference technology from period 1

colnames(result2022) <- c("School", "E2021-T2021", "E2122-T2021", 
                      "E2122-T2122", "E2021-T2122", "PTEC", "TC", "MPI")

kable(result2022, booktabs = T, align = "lccccccc", digits = 3, longtable=T,
               caption = "Benchamrking Pacakge Results (IO-VRS): Academic Year 2020-21 and 2021-22") |>
  kable_styling(latex_options = c("repeat_header","HOLD_position","striped")) |>
  footnote(general = c("2021 = Academic Year 2020-21 and 2122 = Academic Year 2021-22",
                       "E2021-T2021 = Efficiency for academic year 2020-21 with reference technology from academic year 2020-21",
                       "E2122-T2021 = Efficiency for academic year 2021-22 with reference technology from academic year 2020-21",
                       "E2122-T2122 = Efficiency for academic year 2021-22 with reference technology from academic year 2021-22",
                       "E2021-T2122 = Efficiency for academic year 2020-21 with reference technology from academic year 2021-22"))

```


## MPI Results using `DJL` Package
### Academic Year 2018-19 and 2020-21

```{r djl_1821, echo = FALSE, message = FALSE}

library(DJL)

DMUNames <- schooldata[1:34,1] 
mpi_data <- schooldata[,c(1,3,4,5,8,9)]

x0 <- as.matrix(mpi_data [1:34,2])
y0 <- as.matrix(mpi_data [1:34,(3:6)])

x1 <- as.matrix(mpi_data [35:68,2])
y1 <- as.matrix(mpi_data [35:68,(3:6)])

x2 <- as.matrix(mpi_data [69:102,2])
y2 <- as.matrix(mpi_data [69:102,(3:6)])

xdata <- array(c(x0,x1), dim = c(34, 1, 2)) #DJL needs to be array format
ydata <- array(c(y0,y1), dim = c(34, 4, 2)) #DJL needs to be array format

malm_djl1 <- roc.malmquist(xdata, ydata, tm=NULL, dm="dea", rts="vrs", orientation="i",
              g=NULL, wd=NULL, ncv=NULL, env=NULL, cv="convex")

djl_comb1 <- cbind(DMUNames, malm_djl1$cu, malm_djl1$fs, malm_djl1$mi)

djl_res1 <- djl_comb1[,c(1,4,7,10)]
colnames(djl_res1) <- c("School", "PTEC", "TC", "MPI")

kable(djl_res1, booktabs = T, align = "lccc", digits = 3, longtable=T,
               caption = "DJL Pacakge Results (IO-VRS): Academic Year 2018-19 and 2020-21") |>
  kable_styling(latex_options = c("repeat_header","HOLD_position","striped")) 

```


### Academic Year 2020-21 and 2021-22

```{r djl_2022, echo = FALSE, message = FALSE}

library(DJL)

DMUNames <- schooldata[1:34,1] 
mpi_data <- schooldata[,c(1,3,4,5,8,9)]

x0 <- as.matrix(mpi_data [1:34,2])
y0 <- as.matrix(mpi_data [1:34,(3:6)])

x1 <- as.matrix(mpi_data [35:68,2])
y1 <- as.matrix(mpi_data [35:68,(3:6)])

x2 <- as.matrix(mpi_data [69:102,2])
y2 <- as.matrix(mpi_data [69:102,(3:6)])

xdata <- array(c(x1,x2), dim = c(34, 1, 2)) #DJL needs to be array format
ydata <- array(c(y1,y2), dim = c(34, 4, 2)) #DJL needs to be array format


malm_djl2 <- roc.malmquist(xdata, ydata, tm=NULL, dm="dea", rts="vrs", orientation="i",
              g=NULL, wd=NULL, ncv=NULL, env=NULL, cv="convex")

djl_comb2 <- cbind(DMUNames, malm_djl2$cu, malm_djl2$fs, malm_djl2$mi)

djl_res2 <- djl_comb2[,c(1,4,7,10)]
colnames(djl_res2) <- c("School", "PTEC", "TC", "MPI")

kable(djl_res2, booktabs = T, align = "lccc", digits = 3, longtable=T, escape=F,
               caption = "DJL Pacakge Results (IO-VRS): Academic Year 2020-21 and 2021-22") |>
  kable_styling(latex_options = c("repeat_header","HOLD_position","striped")) 

```


## MPI Results using `deaR` Package
### Academic Year 2018-19 and 2020-21

```{r, echo = FALSE, message = FALSE}

library(deaR)
library(dplyr)



all_data1821 <- as.data.frame(schooldata[1:68, c(1,3,4,5,8,9)]) |>
  mutate(Year = rep(c(1,2), each =34)) |>
  select(Year, everything())
  
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}

all_data_malm1821 <- make_malmquist(all_data1821,
                               percol = 1,
                               arrangement = "vertical",
                               dmus = 2,
                               inputs = 3,
                               outputs = 4:7)
                            
```

```{r dear_1821, echo = FALSE, message = FALSE}

result_gr1821 <- deaR::malmquist_index(all_data_malm1821,
                                   orientation = "io",
                                   rts = "vrs",
                                   type1 = "cont",
                                   type2 = "fgnz")

res_mi_gr1821 <- t(rbind(result_gr1821$pech,
                     result_gr1821$tc, result_gr1821$sech, result_gr1821$mi))

colnames(res_mi_gr1821) <- c("PTEC", "TC", "SEC", "MPI")

kbl (res_mi_gr1821, booktabs = T, digits = 3, align = 'c', longtable = T,
     caption = "deaR Pacakge Results (IO-VRS): Academic Year 2018-19 and 2020-21") |>
  kable_styling(latex_options = c("HOLD_position", "striped", "repeat_header"))
```

### Academic Year 2020-21 and 2021-22

```{r, echo = FALSE, message = FALSE}


all_data2022 <- as.data.frame(schooldata[35:102, c(1,3,4,5,8,9)]) |>
  mutate(Year = rep(c(2,3), each =34)) |>
  select(Year, everything())
  
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}

all_data_malm2022 <- make_malmquist(all_data2022,
                               percol = 1,
                               arrangement = "vertical",
                               dmus = 2,
                               inputs = 3,
                               outputs = 4:7)
                            
```

```{r dear_2022, echo = FALSE, message = FALSE}

result_gr2022 <- deaR::malmquist_index(all_data_malm2022,
                                   orientation = "io",
                                   rts = "vrs",
                                   type1 = "cont",
                                   type2 = "fgnz")

res_mi_gr2022 <- t(rbind(result_gr2022$pech,
                     result_gr2022$tc, result_gr2022$sech, result_gr2022$mi))

colnames(res_mi_gr2022) <- c("PTEC", "TC", "SEC", "MPI")

kbl (res_mi_gr2022, booktabs = T, digits = 3, align = 'c', longtable = T,
     caption = "deaR Pacakge Results (IO-VRS): Academic Year 2020-21 and 2021-22") |>
  kable_styling(latex_options = c("HOLD_position", "striped", "repeat_header"))
```

## MPI Results using `MultiplierDEA` Package (IO-CRS) 

### Academic Year 2018-19 and 2020-21 

```{r appendix_data18_21, echo = FALSE}

schooldata <- read_csv("D:/PSU/DEA/BSD DEA Project/ETM 506/MPI Project/Processed Data/MPI_BDS_data.csv", show_col_types=F)

years <- c(rep("1819", 34), rep("2021", 34), rep("2122", 34))

sdata <- as.data.frame(schooldata[,c(1,3,4,5,8,9)]) |>
  mutate(A_Year = years) |>
  mutate(School = substr(School, 1, nchar(School)-4))

data18_21 <- sdata[1:68,]

rownames(data18_21) <- NULL
```

```{r , echo = FALSE}


append_mpi_es1 <- MultiplierDEA::MPI(Dataset = data18_21, DMU_colName = "School", 
             IP_colNames = "Tot_Exp", 
             OP_ColNames = c( "Dis_Stu", "Meal_Elig", "ELA_Prof", "Math_Prof"),
             Period_ColName = "A_Year", Periods = c(1819, 2021),
             rts = "crs", orientation = "input", scale = T) #Scale=TRUE if CRS

```

```{r appendix_result_18_21, echo = FALSE}
append_res_es1 <- cbind(as.numeric(append_mpi_es1$et1t1.crs), #Efficiency for period 1 with reference technology from period 1
                 as.numeric(append_mpi_es1$et1t2.crs), #Efficiency for period 2 with reference technology from period 1
                 as.numeric(append_mpi_es1$et2t2.crs), #Efficiency for period 2 with reference technology from period 2
                 as.numeric(append_mpi_es1$et2t1.crs), #Efficiency for period 1 with reference technology from period 2
                 as.numeric(append_mpi_es1$tec),       #tec for CRS
                 as.numeric(append_mpi_es1$tc),
                 as.numeric(append_mpi_es1$m.crs))

colnames(append_res_es1) <- c("E1819-T1819", "E2021-T1819", 
                      "E2021-T2021", "E1819-T2021", "PTEC", "TC", "MPI")

rownames(append_res_es1) <- append_mpi_es1$DMU

kbl(append_res_es1, digits = 3,  booktabs=T, align ="ccccccc", longtable=T,
    caption="MultiplierDEA Package Results (IO-CRS): Academic Year 2018-19 and 2020-21") |>
  kable_styling(latex_options = c("HOLD_position", "repeat_header", "striped")) |>
  footnote(general = c("1819 = Academic Year 2018-19 and 2021 = Academic Year 2020-21",
                       "E1819-T1819 = Efficiency for academic year 2018-19 with reference technology from academic year 2018-19",
                       "E2021-T1819 = Efficiency for academic year 2020-21 with reference technology from academic year 2018-19",
                       "E2021-T2021 = Efficiency for academic year 2020-21 with reference technology from academic year 2020-21",
                       "E1819-T2021 = Efficiency for academic year 2018-19 with reference technology from academic year 2020-21"))

```

### Academic Year 2020-21 and 2021-22 

```{r appendix_data20_22, echo = FALSE}

schooldata <- read_csv("D:/PSU/DEA/BSD DEA Project/ETM 506/MPI Project/Processed Data/MPI_BDS_data.csv", show_col_types=F)

years <- c(rep("1819", 34), rep("2021", 34), rep("2122", 34))

sdata <- as.data.frame(schooldata[,c(1,3,4,5,8,9)]) |>
  mutate(A_Year = years) |>
  mutate(School = substr(School, 1, nchar(School)-4))

data20_22 <- sdata[35:102,]

rownames(data20_22) <- NULL
```

```{r , echo = FALSE}


append_mpi_es2 <- MultiplierDEA::MPI(Dataset = data20_22, DMU_colName = "School", 
             IP_colNames = "Tot_Exp", 
             OP_ColNames = c( "Dis_Stu", "Meal_Elig", "ELA_Prof", "Math_Prof"),
             Period_ColName = "A_Year", Periods = c(2021, 2122),
             rts = "crs", orientation = "input", scale = T) #Scale=TRUE if CRS

```

```{r appendix_result_20_22, echo = FALSE}
append_res_es2 <- cbind(as.numeric(append_mpi_es2$et1t1.crs), #Efficiency for period 1 with reference technology from period 1
                 as.numeric(append_mpi_es2$et1t2.crs), #Efficiency for period 2 with reference technology from period 1
                 as.numeric(append_mpi_es2$et2t2.crs), #Efficiency for period 2 with reference technology from period 2
                 as.numeric(append_mpi_es2$et2t1.crs), #Efficiency for period 1 with reference technology from period 2
                 as.numeric(append_mpi_es2$tec),       #tec for CRS
                 as.numeric(append_mpi_es2$tc),
                 as.numeric(append_mpi_es2$m.crs))

colnames(append_res_es2) <- c("E2021-T2021", "E2122-T2021", 
                      "E2122-T2122", "E2021-T2122", "PTEC", "TC", "MPI")
rownames(append_res_es2) <- append_mpi_es2$DMU

kbl(append_res_es2, digits = 3,  booktabs=T, align ="ccccccc", longtable=T,
    caption="MultiplierDEA Package Results (IO-CRS): Academic Year 2020-21 and 2021-22") |>
  kable_styling(latex_options = c("HOLD_position", "repeat_header", "striped")) |>
  footnote(general = c("2021 = Academic Year 2020-21 and 2122 = Academic Year 2021-22",
                       "E2021-T2021 = Efficiency for academic year 2020-21 with reference technology from academic year 2020-21",
                       "E2122-T2021 = Efficiency for academic year 2021-22 with reference technology from academic year 2020-21",
                       "E2122-T2122 = Efficiency for academic year 2021-22 with reference technology from academic year 2021-22",
                       "E2021-T2122 = Efficiency for academic year 2020-21 with reference technology from academic year 2021-22"))

```
